CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
caption
paper

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
% styles for flowcharts
\tikzstyle{machine} = [star, star points=7, star point ratio=0.8, draw, text width=5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{data} = [trapezium, trapezium left angle=70, trapezium right angle=-70, draw,text centered]
\tikzstyle{process} = [rectangle, draw, text width=5em, text centered, rounded corners, minimum height=4em]

@@

@@

\begin{figure}
 \label{diagram}
 \begin{center}
  \begin{tikzpicture}[node distance=2.5cm, auto, >=stealth]
   % nodes
   \node[data] (Q)                                      {Question};
   \node[process] (ch) [below of=Q]                     {Chunker};
   \node[data] (docs) [right of=ch]                     {Documents};
   \node[process] (fil) [below of=ch]                     {Filter};
   \node[process] (a2) [below of=fil]                    {Answer Evaluator};
   \node[process] (a1) [left of=a2]                     {Answer Evaluator};
   \node[process] (a3) [right of=a2]                    {Answer Evaluator};
   \node[machine] (as) [below of=a2]                    {Score aggregator};
   \node[data] (A) [below of=as]                        {Answer};

   % edges
   	\draw[->] (Q) to (ch);
	\draw[->] (docs) to (ch);
	\draw[->] (ch) to (fil);
	\draw[->] (fil.south) to [out=270, in=90] (a1);
	\draw[->] (fil.south) to [out=270, in=90] (a2);
	\draw[->] (fil.south) to [out=270, in=90] (a3);
	\draw[->] (Q.west) to [out=180, in=180] (a1);
	\draw[->] (Q.west) to [out=180, in=180] (a2);
	\draw[->] (Q.west) to [out=180, in=180] (a3);
	\draw[->] (a1.south) to [out=270, in=135] (as);
	\draw[->] (a2.south) to [out=270, in=90] (as);
	\draw[->] (a3.south) to [out=270, in=45] (as);
	\draw[->] (as) to (A);
  \end{tikzpicture}
  \caption{Data Flow}
  \label{flowchart}
 \end{center}
\end{figure}

@@

@@

\subsection{Walk through of one question}
\begin{itemize}
\item Initial setup of the Q/A system
    \begin{itemize}
    \item We collect all the documents that may contain the answer for all qids (20 documents per qid)
    \item We then run the chunker on the document text creating answer candidate phrases
    \item We save the chunker results to a set of files
    \end{itemize}
\item We are given a question id
\item We retrieve the question text from the provided input file
\item We read the chunker results 
    \begin{itemize}
    \item We filter out all candidate answers that are not noun phrases
    \item We also filter out candidate answers not within 50 bytes of the aligned question in the document
    \end{itemize}
\item We feed the filtered answers through our answer evaluators specifically
    \begin{itemize}
    \item punctuation location
    \item novelty factor
    \item A combination of both
    \end{itemize}
\item The scores of the evaluators are fed into the supervised classification algorithm
    \begin{itemize}
    \item Spectral Regression Discriminant Analysis 
    \item This gives us a confidence measure
    \end{itemize}
\item Sort by confidence measure 
\item In descending order by confidence measure, pack them into 50-byte answers which are our final outputs
\item The answers are then passed into our scorer
\end{itemize}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
% styles for flowcharts
\tikzstyle{machine} = [star, star points=7, star point ratio=0.8, draw, text width=5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{data} = [trapezium, trapezium left angle=70, trapezium right angle=-70, draw,text centered]
\tikzstyle{process} = [rectangle, draw, text width=5em, text centered, rounded corners, minimum height=4em] 
\tikzstyle{null} = []

@@

CAT-DWAM is a system that uses spectral regression discriminant analysis, a
supervised classification algorithm, to assemble and analyze a variety of
disparate indicators for accuracy.

By using a machine learner, we aim to answer questions without relying on
hand-written judgements of rules, although for performance reasons we were
forced to use some rules to narrow down the input set.

@@

\begin{figure}
 \label{diagram}
 \begin{center}
  \begin{tikzpicture}[node distance=2.5cm, auto, >=stealth]
   % nodes
   \node[data] (Q)                                      {Question};
   \node[process] (ch) [below of=Q]                     {Chunker};
   \node[null] (xx) [right of=ch]                     {};
   \node[data] (docs) [right of= xx]                     {Documents};
   \node[process] (fil) [below of=ch]                     {Filter};
   \node[process] (a2) [below of=fil]                    {Answer Evaluator};
   \node[process] (a1) [left of=a2]                     {Answer Evaluator};
   \node[process] (a3) [right of=a2]                    {Answer Evaluator};
   \node[machine] (as) [below of=a2]                    {Score aggregator};
   \node[data] (A) [below of=as]                        {Answer};

   % edges
   	\draw[->] (Q) to (ch);
	\draw[->] (docs) to (ch);
	\draw[->] (ch) to (fil);
	\draw[->] (fil.south) to [out=270, in=90] (a1);
	\draw[->] (fil.south) to [out=270, in=90] (a2);
	\draw[->] (fil.south) to [out=270, in=90] (a3);
	\draw[->] (Q.east) to [out=0, in=0] (fil);
	\draw[->] (Q.west) to [out=180, in=180] (a1);
	\draw[->] (Q.west) to [out=180, in=180] (a2);
	\draw[->] (Q.west) to [out=180, in=180] (a3);
	\draw[->] (a1.south) to [out=270, in=135] (as);
	\draw[->] (a2.south) to [out=270, in=90] (as);
	\draw[->] (a3.south) to [out=270, in=45] (as);
	\draw[->] (as) to (A);
  \end{tikzpicture}
  \caption{Data Flow}
  \label{flowchart}
 \end{center}
\end{figure}

@@

Unfortunately, the SRDA system attempted to allocate tens of gigabytes of RAM in
order to perform its analysis of the training data, and crashed.  So we were
forced to thin the candidates.

@@

\subsection{Walk through of one question}
\begin{itemize}
\item Initial setup of the Q/A system
    \begin{itemize}
    \item We collect all the documents that may contain the answer for all qids (20 documents per qid)
    \item We then run the chunker on the document text creating answer candidate phrases
    \item We save the chunker results to a set of files
    \end{itemize}
\item We are given a question id
    \begin{itemize}
    \item 10025
    \end{itemize}
\item We retrieve the question text from the provided input file
    \begin{itemize}
    \item "Where is Bolivia?"
    \end{itemize}
\item We read the chunker results 
    \begin{itemize}
    \item We filter out all candidate answers that are not noun phrases
    \item We also filter out candidate answers not within 50 bytes of the aligned question in the document
    \end{itemize}
\item We feed the filtered answers through our answer evaluators specifically
    \begin{itemize}
    \item punctuation location
    \item novelty factor
    \item A combination of both
    \end{itemize}
\item The scores of the evaluators are fed into the supervised classification algorithm
    \begin{itemize}
    \item Spectral Regression Discriminant Analysis 
    \item This gives us a confidence measure
    \end{itemize}
\item Sort by confidence measure 
\item In descending order by confidence measure, pack them into 50-byte answers which are our final outputs
\item The answers are then passed into our scorer
\end{itemize}
